Designing Types for R, Empirically

### 2020-10-05 paper/main.tex
minor
acks

\documentclass[acmsmall, screen,review]{acmart}
\setlength{\pdfpagewidth}{8.5in}
\setlength{\pdfpageheight}{11in}
%\settopmatter{printfolios=true,printccs=true,printacmref=true}

@@

%
%
%
%
% \subsection{Discussion}

% As a closing point of discussion, we would like to highlight an alternate strategy for unifying class types that we considered.
% Recall that in our proposed type annotation language, classes are represented as \CLASS{{\tt A}} for something of class {\tt A}, and \CLASS{{\tt A}, {\tt B}} for something with two classes {\tt A} and {\tt B}.

% During the robustness phase of our evaluation, we noted a number of class-based type errors such as a \CLASS{{\tt data.frame}} being passed to an argument expecting, e.g., a \CLASS{{\tt data.frame}, {\tt tbl}, {\tt tbl\_df}}.
% This represents something of a limitation of our approach, as data frames and {\tt dplyr} tibbles are related and convertible (you can think of a tibble as a subclass of a data frame)---a fact not represented by our types.
% One option to mitigate this would be to include a type such as \CLASS{{\tt data.frame}, ...} that must include {\it at least} the {\tt data.frame} class, but this would not altogether solve this problem.
% For one, to generate this type we would either need to a) include some type hierarchy in our type system, which is outside of the scope of this work, or b) somehow infer the type with \typetracer.
% To create this type, \typetracer would have to observe values of {\it both} type \CLASS{{\tt data.frame}} and \CLASS{{\tt data.frame}, {\tt tbl}, {\tt tbl\_df}}, which would not solve the aforementioned problem as many {\tt dplyr} functions are only called with tibbles.

% Further, the data table, another data frame alternative, while being coercible to and from a data frame, only has \CLASS{{\tt data.table}} (not including {\tt data.frame} as part of its class).
% This alternate class type would also not adequately capture this behaviour, and even worse, if a \CLASS{{\tt data.frame}} and \CLASS{{\tt data.table}} were to co-occur in an argument type, we would unify it to \CLASS{...}, which is not very informative.

% For these reasons, we believe our unification strategy for class types to be adequate until we extend our type system to handle R's wild and varied object orientation frameworks.

%
%
%
%
%
%
\section{Conclusion}

@@

\section*{Acknowledgements}

This work was partially funded by NSERC.

>>>>

\documentclass[acmsmall, screen]{acmart}
\setlength{\pdfpagewidth}{8.5in}
\setlength{\pdfpageheight}{11in}
%\settopmatter{printfolios=true,printccs=true,printacmref=true}

@@

%
%
%
%
\section{Conclusion}

@@

\begin{acks}
This work has received funding from the \grantsponsor{ONR}{Office of
  Naval Research (ONR)}{} award \grantnum{ONR}{503353}, the
\grantsponsor{NSF}{National Science Foundation}{} awards
\grantnum{NSF}{1759736}, \grantnum{NSF}{1544542},
\grantnum{NSF}{1925644}, and \grantnum{NSF}{1910850}, the
\grantsponsor{BC}{Czech Ministry of Education, Youth and Sports from
  the Czech Operational Programme Research, Development, and
  Education}{}, under grant agreement No.
\grantnum{BC}{CZ.02.1.01/0.0/0.0/15\_003/0000421}, and the
\grantsponsor{ELE}{European Research Council (ERC) under the European
  Union's Horizon 2020 research and innovation programme}{}, under
grant agreement No.  \grantnum{ELE}{695412}. This work was partially
funded by NSERC.
\end{acks}
